Inferring generation-interval distributions from contact tracing data

### 2018-09-21 doc/network.tex
add comment

The difference between conditional and intrinsic generation-interval distribution can be best demonstrated by simulating stochastic infection processes on a small tree network -- a single infected individual is connected to multiple susceptible individuals but susceptibles are not connected with each other -- with artificially high $\RR$ (Figure~\ref{fig:local}).
We observe that the distribution of realized generation times matches with the conditional generation-interval distribution, whereas the distribution of contact times matches with the intrinsic generation-interval distribution.
On the other hand, if a stochastic infection processes are simulated on a small homogeneous network with all else being equal, the distribution of generation times is even shorter than the effective generation intervals because a susceptible individual may be contacted by multiple infectors (and only the first contact gives rise to infection).
\jd{Let's think about how to explain this. In particular, the first one is where we have our correction that works \ldots}.
Hence, we expect there to be varying degrees of local depletion of susceptibles in a heterogeneous contact structure and the accurate measurement of generation interval will be more difficult.

>>>>

The difference between conditional and intrinsic generation-interval distribution can be best demonstrated by simulating stochastic infection processes on a small tree network -- a single infected individual is connected to multiple susceptible individuals but susceptibles are not connected with each other -- with artificially high $\RR$ (Figure~\ref{fig:local}).
We observe that the distribution of realized generation times matches with the conditional generation-interval distribution, whereas the distribution of contact times matches with the intrinsic generation-interval distribution.
On the other hand, if a stochastic infection processes are simulated on a small homogeneous network with all else being equal, the distribution of generation times is even shorter than the effective generation intervals because a susceptible individual may be contacted by multiple infectors (and only the first contact gives rise to infection).
\jd{Let's think about how to explain this. In particular, the first one is where we have our correction that works \ldots}.
\swp{I think things are clearer when we introduce conditional kernel?}
Hence, we expect there to be varying degrees of local depletion of susceptibles in a heterogeneous contact structure and the accurate measurement of generation interval will be more difficult.
